---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Load the releavent datasets 

```{r}setwd("C://R//RepData_PeerAssessment1")
activity <- read.csv("activity.csv")
names(activity)
```

## What is mean total number of steps taken per day?

```{r}
activity <- read.csv("activity.csv")
stepsperday <- aggregate(steps ~ date, activity, sum, na.rm=TRUE)
barplot(stepsperday$steps, names.arg=stepsperday$date,xlab="Total steps per day", ylab="Interval")
```

The mean and median steps are derived as below:

```{r}
median(stepsperday$steps)
mean(stepsperday$steps)
```

## What is the average daily activity pattern?

Average is basically the mean by interval. So using the above logic and use plot function with type as "l""

```{r}
activity <- read.csv("activity.csv")
stepsinterval <- aggregate(steps ~ interval, activity, mean, na.rm=TRUE)
plot(stepsinterval, type="l")
```

To get the max of 5-min interval 
```{r}
stepsinterval$interval[which.max(stepsinterval$steps)]
```


## Imputing missing values
Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
activity <- read.csv("activity.csv")
missing <- sum(is.na(activity))
missing
```

Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.

Create a new dataset that is equal to the original dataset but with the missing data filled in and plot in barplot 


```{r}
activity <- read.csv("activity.csv")
stepsinterval <- aggregate(steps ~ interval, activity, mean)
activity <- merge(activity, stepsinterval, by="interval", suffixes = c("",".y"))
getNAs <- is.na(activity$steps)
activity$steps[getNAs] <- activity$steps.y[getNAs]
activity <- activity[,c(1:3)]
activity

stepsperday <- aggregate(steps ~ date, activity, sum)
barplot(stepsperday$steps, names.arg=stepsperday$date,xlab="Total steps per day", ylab="Interval")

mean(stepsperday$steps)
median(stepsperday$steps)
```



## Are there differences in activity patterns between weekdays and weekends?
